Alberta's Electricity Market

### 2022-04-28 paper/paper_draft.tex
fixing some bits
update

%%%% TITLE %%%%
\title{Marginal and Average Carbon Price Pass-Through\thanks{We are grateful to Sam Harrison for excellent
research assistance. We thank seminar and conference participants at the AERE Summer Meetings for comments and suggestions. Financial support for this work was provided by the Future Energy Systems Canada First Research Excellence Fund grant held by the University of Alberta.}
}

@@

%%%% ABSTRACT %%%%
\begin{abstract}
\noindent We evaluate the response of wholesale power market participants in Alberta to a series of changes in greenhouse gas (GHG) emissions policies.  Between 2015 and 2019, legislative changes have affected carbon price levels, the rates of output-based allocations of emissions credits, and the coverage of carbon pricing across facilities of different sizes, creating variation in average and marginal carbon prices both across and within facility types and across and within portfolios held by major players in Alberta's wholesale power market. We exploit this variance in treatment to provide unique evidence of offer response to carbon pricing in power markets. We show that even after adjusting for costs imposed by carbon policies at the facility level, statistically significant changes in portfolio-level offer curves were induced leading to a shift in the merit order toward gas and away from coal which exceeded that which would have been predicted by carbon prices alone.\\ \\
Keywords: climate change, carbon pricing, electricity, coal\\ \\
JEL classification: Q3, Q4, Q54
\end{abstract}

>>>>

%%%% TITLE %%%%
\title{Carbon Price Pass-Through in Alberta's Power Market\thanks{We are grateful to Sam Harrison for excellent
research assistance. We thank seminar and conference participants at the AERE Summer Meetings for comments and suggestions. Financial support for this work was provided by the Future Energy Systems Canada First Research Excellence Fund grant held by the University of Alberta.}
}

@@

%%%% ABSTRACT %%%%
\begin{abstract}
\noindent\\ \\
Keywords: climate change, carbon pricing, electricity, coal\\ \\
JEL classification: Q3, Q4, Q54
\end{abstract}
